\textbf{BibTrek: A Graph Visualization Tool for Cybersecurity Publications}

### 2019-07-30 article/article.tex
Article completely restructured

\section{Evaluation}
\subsection{Tests}
We have tested our application for a set of author and publication queries whilst locally running Neo4j using a computer with the following specs:
\begin{itemize}
\item \textbf{OS:} 64-bit Ubuntu 18.04.2 LTS GNU/Linux 
\item \textbf{CPU:} Intel Core 2 Duo P8700 @ 2.534GHz 
\item \textbf{GPU:} Intel Mobile 4 Series Chipset
\item \textbf{RAM:} 4096MB @ 1066Mhz 
\end{itemize}
BibTrek successfully processed and inserted all nodes and relations into the Neo4j database. We were able to search for any added data with ease. However, the data retrieved from the DBLP database might present a variable number of field attributes. Since we are following a fixed attribute structure for our node data, some of these fields are ignored. Future versions should consider adding these fields dynamically, we further these considerations on the Future Work section of this article.
\subsection{Functionalities}
At the current moment we can choose only to retrieve data from the DBLP publication. Nonetheless, future versions will include an option to query the ArXiV library, IEEE Xplore and any combination of these. Choosing the DBLP option we are able to pick whichever option suits our interests the most. At the current time we are able to query by author's name, author's publications and publication title. Once queried, BibTrek presents us the data that it has been able to retrieve. The user is then given the option to mark whichever of the retrieved information will be stored in the Neo4j graph database. The marked options are then stored on the graph with their appropriate relations. It is possible at any given moment to cancel any of the above mentioned procedures.

@@

\section{Acknowledgements}
The writer of this article would like to thank Professor Miguel L. Pardal and INESC-ID for having invited him for a one month summer-internship program. With this program the writer learned highly valuable knowledge in the areas of cybersecurity, distributed systems and scientific research from multiple researcher peers. Non only that but also acquired a greater work ethic. With this being said he has the utmost gratitude for having been part of this project from which he has learned immensely from.

>>>>

\section{Evaluation}
In this section we discuss the tests that were done using the application to query a web based library and the parsing and processing of the results. Furthermore we elaborate on the functionalities present in BibTrek. Finally, we list the commands available on the program's terminal console.

\subsection{Tests}
We have tested our application for a set of author and publication queries whilst locally running Neo4j using a computer with the following specs:
\begin{itemize}
\item \textbf{OS:} 64-bit Ubuntu 18.04.2 LTS GNU/Linux 
\item \textbf{CPU:} Intel Core 2 Duo P8700 @ 2.534GHz 
\item \textbf{GPU:} Intel Mobile 4 Series Chipset
\item \textbf{RAM:} 4096MB @ 1066Mhz 
\end{itemize}
BibTrek successfully processed and inserted all nodes and relations into the Neo4j database. We were able to search for any added data with ease. However, the data retrieved from the DBLP database might present a variable number of field attributes. Since we are following a fixed attribute structure for our node data, some of these fields are ignored. Future versions should consider adding these fields dynamically, we further these considerations on the Future Work section of this article.
\subsection{Functionalities}
At the current moment we can choose only to retrieve data from the DBLP publication. Nonetheless, future versions will include an option to query the ArXiV library, IEEE Xplore and any combination of these. Choosing the DBLP option we are able to pick whichever option suits our interests the most. At the current time we are able to query by author's name, author's publications and publication title. Once queried, BibTrek presents us the data that it has been able to retrieve. The user is then given the option to mark whichever of the retrieved information will be stored in the Neo4j graph database. The marked options are then stored on the graph with their appropriate relations. It is possible at any given moment to cancel any of the above mentioned procedures.
\subsection{Command-line interface}
Here we present a detailed functioning of the interface. We elaborate on every avaible option for the user to interact with, and explain the way the system interacts with the web based library.
\\[1\baselineskip]
Once the application is started we are presented with the choice of either selecting the option to query the DBLP database or exit the program. Once the first is chosen, it is presented to us the available options to query the database. These options are the following:

\begin{itemize}
\item \textbf{Query by author}. Choosing it, we are required to type the name of the author we want to search. Afterwards BibTrek fetches us, all authors present in the DBLP database with a similar name to the one that we have inserted previously. We are then told to pick which of the fetched authors we want to insert into the database.
\item \textbf{Query by publication's title.}. Here, we type the title of the publication we want to find. After querying DBLP, we are presented with all the available publications bearing a similar title. We are then required to pick which of the displayed publications we want to add to our local database.
\item \textbf{Query by author's publication}. Similar to the first option, we type the author's name. BibTrek then fetches us all the available authors in the system. We are then asked to choose which of the fetched authors we want to search publications of. After doing so, the system fetches us all the available publications for the chosen authors incrementally. Finally, we are required to choose which of the displayed publications we want to insert into the system
\end{itemize}
It is worth mentioning that any given step of the above procedures we can choose either the option of adding all the displayed information to our data set or exit the current state of the system.

@@

\section{Acknowledgements}
The writer of this article would like to thank Professor Miguel L. Pardal and INESC-ID for having invited him for a one month summer-internship program and for the reviewing of this article. With this program the writer learned highly valuable knowledge in the areas of cybersecurity, distributed systems and scientific research from multiple researcher peers. Non only that but also acquired a greater work ethic. With this being said he has the utmost gratitude for having been part of this project from which he has learned immensely from.
